Seismic Time Series Analysis\\Statistics for Spatio-Temporal Data\\\textit{-- project draft --}

### 2020-06-06 project.Rmd
add spencer filter

>>>>

```{r trend Spencer}
weights.s <- c(-3,-6,-5,3,21,46,67)
weights.s <- c(weights.s, 74, rev(weights.s))
weights.s <- weights.s/sum(weights.s)
trend.s <- stats::filter(seasonality.aggregate(seis.h.train), side=2, filter=weights.s)

plots <- show_overlap_and_diff(
  dec.addi$trend, trend.s, xlab=seasonality.xlab,
  base.desc = "additive decomposition trend",
  compare.desc = "Spencer's 15-point MA",
  overlap.ylab = "Trend (nm)",
  diff.title = "Difference between trends",
  diff.ylab = "nm", diff.ylab.sec="% over trend span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
